---
title: "Recreate visR example"
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(survival)
library(tidyverse)
library(here)
library(dplyr)
library(tidyr)
library(survival)
library(ggplot2)
library(broom)
library(purrr)
library(gtable)
library(cowplot)
library(plotly)
library(survminer)

source(here("R","vr_KM_est.R"))
source(here("R","/vr_plot.R"))
source(here("R","tidyme.R"))
source(here("R","add_CI.R"))
source(here("R","add_CNSR.R"))
source(here("R","add_COX_HR.R"))
source(here("R","add_risktable.R"))
source(here("R","utilities.R"))
source(here("R","get_quantile.R"))
source(here("R","vr_plotly.R"))
```


Global constants. 

```{r}
# Constants
DATASET <-
  paste0("NCCTG Lung Cancer Dataset (from survival package ",
         packageVersion("survival"),
         ")")

# Globql formatting options
options(digits = 3)

# Global ggplot settings
theme_set(theme_classic())

# Global table settings
options(DT.options = list(
  pageLength = 10,
  language = list(search = 'Filter:'),
  scrollX = TRUE
))
```


Load the data set.

```{r}
### Data set
data(lung)
```


Prepare the data set. Also convert to CDISC. 

Important variavles:

* status:	censoring status 1=censored, 2=dead
* time:	Survival time in days

For, CDISC convert those variables as follows:

* AVAL - Analysis value (time to event [days])
* CNSR - Censoring (0 = Event, 1 = censored)


**Here, the only additional step from the original example is the renaming of time to AVAL.**

```{r}

lung_cohort <- lung %>%
  rename(ECOG = ph.ecog,
         Karnofsky = ph.karno,
         institution = inst) %>%
  mutate(
    patid = paste0("Pat", row_number()),
    institution = factor(institution),
    sex = factor(if_else(sex == 1, "male", "female")),
    ECOG = factor(
      case_when(
        ECOG == 0 ~ "0 asymptomatic",
        ECOG == 1 ~ "1 ambulatory",
        ECOG == 2 ~ "2 in bed less than 50% of day",
        ECOG == 3 ~ "3 in bed more than 50% of day",
        ECOG == 4 ~ "4 bedbound",
        ECOG == 5 ~ "5 dead"
      )
    ),
    dx_age_group = factor(
      case_when(
        age < 30 ~ "< 30y",
        age >= 30 &
          age <= 50 ~ "30-50y",
        age > 50 &
          age <= 70 ~ "51-70y",
        age > 70 ~ "> 70y"
      ),
      levels = c("< 30y", "30-50y", "51-70y", "> 70y")
    ),
    AVAL = time, 
    CNSR = case_when(status == 1 ~ 1,
                     status == 2 ~ 0)      #replacing status = if_else(status == 1, 0, 1)
  ) %>%
  select(-meal.cal,-pat.karno)
```

Check the variables are transformed ok. 

```{r}
lung_cohort %>% glimpse()
```



Current visR api:

```{r, eval=FALSE}
surv_eq <- "survival::Surv(time, status) ~ sex"
vr_kaplan_meier(
  lung_cohort,
  equation = surv_eq,
  data_source = DATASET,
  time_unit = "days",
  title = "Comparison of survival in male and female lung cancer patients"
)
```






Fit model and store object 

```{r}
vr_km_obj <- 
  vr_KM_est(data = lung_cohort, strata = "sex") 
```



## plot with risk table 

```{r}
vr_km_obj %>%
  vr_plot(legend.position = "top") %>%
  add_CI() %>%
  add_CNSR(shape = 3, size = 2) %>%
  add_risktable(min_at_risk = 1)
```


TODO: 

* **CHECK** why there is a difference in the risk numbers compared to the visR example. 

Original data and using Survival to perform cross check test. 

```{r}
km <- survfit(Surv(time, status == 2) ~ sex, data = lung) 

summary(km, times = c(0, 100, 200, 300, 400, 500, 600, 700, 800, 900))

```

```{r}
ggsurvplot(
   km,                     # survfit object with calculated statistics.
   data = lung,  # data used to fit survival curves. 
   risk.table = TRUE,         # show risk table.
   break.time.by = 100       # break X axis in time intervals by 500.
   
)
```

Crude way to summarise the KM estimates.

```{r}
vr_km_obj 
```

How to get p-values and Cox PH HR estimates using Survial

```{r}
survdiff(Surv(time, status == 2) ~ sex, data = lung, rho = 0)
coxph(Surv(time, status == 2) ~ sex , data = lung)
```


